---
title: "golite"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation

Install the package with:

```{r,eval=FALSE}
library(devtools)
install_github("ZhenWei10/golite")
```

## Run GO enrichment analysis

The necessary input of GOEA should be the gene set gene ID, background gene ID, and the [orgDb object](http://www.bioconductor.org/packages/release/data/annotation/html/org.Hs.eg.db.html).

```{r,message=FALSE}
library(golite)
library(magrittr)
library(org.Hs.eg.db)
```

Get example randomly sampled gene ids for background and gene set.

```{r,message  = F,cache=F, warning=FALSE}
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
txdb = TxDb.Hsapiens.UCSC.hg19.knownGene
all_eids_hg19 <- names(genes(txdb))

set.seed(1)
eids_bg <- sample(all_eids_hg19, 3500)
eids_set <- sample(eids_bg,300)
```

Run GO enrichment analysis given gene set and background.

```{r}
GOEA(gene_set = eids_set,
     back_ground = eids_bg,
     orgDb = org.Hs.eg.db,
     interpret_term = T) %>% head(.,10) %>% knitr::kable(.,"markdown")
```

The function can be vectorized, i.e. the input can be a `list` of multiple gene sets.

```{r}
eids_sets <- lapply(1:10,function(x) sample(eids_bg,300)) 

GOEA(gene_set = eids_sets,
     back_ground = eids_bg,
     orgDb = org.Hs.eg.db) %>% summary
```


## Run GO slim enrichment analysis

GO slim is a subset of GO terms that can be defined at [here](http://geneontology.org/ontology/subsets/).

```{r}
GOEA(gene_set = eids_set,
     back_ground = eids_bg,
     orgDb = org.Hs.eg.db,
     interpret_term = T,
     GO_Slim = T)  %>% head(.,10) %>% knitr::kable(.,"markdown")
```

you could set `EASE_score = TRUE` to get a more conservative p value.

For more information of EASE, please see [here](https://david.ncifcrf.gov/helps/functional_annotation.html#fisher).

```{r}
GOEA(gene_set = eids_sets,
     back_ground = eids_bg, 
     orgDb = org.Hs.eg.db,
     GO_Slim = T,
     EASE_Score = F) %>% lapply(.,function(x)x$p) %>% unlist %>% hist(main = "normal hypergeometric")

GOEA(gene_set = eids_sets,
         back_ground = eids_bg,
     orgDb = org.Hs.eg.db,
     GO_Slim = T,
     EASE_Score = T) %>% lapply(.,function(x)x$p) %>% unlist %>% hist(main = "EASE score")
```

with any questions, please contact zhen.wei@xjtlu.edu.cn.

```{r}
sessionInfo()
```

